RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

@@

## Plots of top differentially expressed genes
```{r markerGenes, fig.width=15, fig.height=30}

>>>>

#### Correlation between individuals
```{r corr.btw.indivs}
form = ~ (1|CellType) + (1|Batch)
vobj.simple = voomWithDreamWeights(dge, form, info, BPPARAM=SnowParam(12, progressbar=TRUE))

fit.simple = dream(vobj.simple, form, info, BPPARAM=SnowParam(12, progressbar=TRUE))
residCompare = residuals(fit.simple) 
```

@@

## Plots of top differentially expressed genes
```{r markerGenes, fig.width=15, fig.height=40}
